### 2024-01-02 chapters/conclusion.tex
Final updates

\textbf{\Cref{chp:introduction}} introduced the motivational cases of automated medical coding and stroke recognition and used them to exemplify the importance of out-of-distribution detection, and, by extension, representation learning. In the context of these cases, we discussed possible machine learning system designs for decision support and considered potential sources of uncertainty and ideal model behavior. 
The cases form a reference point for the thesis as a whole, connecting its contributions within out-of-distribution detection and representation learning back to practical applications. 
In this conclusion, we will review the studies presented in previous chapters in the context of the discussion of \cref{chp:discussion} and the recent progress in the field, and point to interesting directions of future research. 
As \textbf{\cref{chp:main-contributions}} already details the contributions made by this thesis, we will not reiterate them in detail in this conclusion.

>>>>

\textbf{\Cref{chp:introduction}} introduced the motivational cases of automated medical coding and stroke recognition and used them to exemplify the importance of out"=of"=distribution detection, and, by extension, representation learning. In the context of these cases, we discussed possible machine learning system designs for decision support and considered potential sources of uncertainty and ideal model behavior. 
The cases form a reference point for the thesis as a whole, connecting its contributions within out"=of"=distribution detection and representation learning back to practical applications. 
In this conclusion, we will review the studies presented in previous chapters in the context of the discussion of \cref{chp:discussion} and the recent progress in the field, and point to interesting directions of future research. 
As \textbf{\cref{chp:main-contributions}} already details the contributions made by this thesis, we will not reiterate them in detail in this conclusion.

### 2024-01-02 chapters/paper_review/03_approaches.tex
Fix commas after equations
Final updates

A drawback of APC is that it encodes information only from previous timesteps
and not the entire input.
DeCoAR~\parencite{ling_deep_2020} combines the bidirectionality of the popular NLP model
ELMo~\parencite{peters_deep_2018} and the reconstruction objective of APC to alleviate
this issue and allow encoding information from the entire input. 
It uses a forward LSTM $f_1(\cdot)$ to encode $X_{[1,t]}$ and a backward LSTM
$f_2(\cdot)$ to encode $X_{[t+k,T]}$, where $k>1$: 
\begin{gather}
    H_{[1,t]} = f_1(X_{[1,t]}), \\
    H^\prime_{[t+k,T]} = f_2(X_{[t+k,T]}), \\
    \hat{X}_{[t+1,t+k-1]} = g(h_t, h^\prime_{t+k}) \enspace .
\end{gather}
The input feature vector used in the downstream tasks is the concatenation of
$h_{t}$ and $h^\prime_{t}$.

@@

From a high-level perspective, the training phase of models using masked
reconstruction can be formulated as
\begin{align}
    H &= f(m(X)), \\
    \hat{x}_t &= g(h_{t}), \\
    \mathcal{L}_t &= \lVert \hat{x}_{t} - x_{t} \rVert_1 .
\end{align}
\edit{The exact masking policy defined by $m(\cdot)$ differs from model to model and will be discussed further below.}
The function $f(\cdot)$ is typically a Transformer encoder~\parencite{liu_mockingjay_2020,jiang_improving_2019,liu_masked_2020}, but recurrent neural networks have also been used~\parencite{wang_unsupervised_2020}. \edit{In general, the Transformer encoder architecture has been adopted widely by self"=supervised models for speech within all three surveyed categories.} \edit{The function $g(\cdot)$ is usually a linear projection or a multilayer perceptron (MLP)}. Finally, the loss $\mathcal{L}_t$ is commonly computed only for masked timesteps in order to discourage the model from learning an identity mapping.

The masking policies used in NLP can be adapted to speech by considering a speech \edit{segment} equivalent to a token in a sentence; indeed, the masking strategy of BERT has also been used for speech pre"=training~\parencite{liu_mockingjay_2020}.
In the standard BERT masking policy, each token is masked independently at random. However, for speech, masking a single \edit{sample or spectrogram frame results in a largely} trivial reconstruction task \edit{since, as discussed in %\cref{par:apc}
the paragraph on autoregressive prediction, the smoothness of audio signals may encourage the model to learn to simply interpolate neighboring frames.} Therefore it is common to mask chunks of consecutive frames~\parencite{liu_mockingjay_2020,jiang_further_2021}.

@@

Some studies explore alternatives to masking the input directly. In non"autoregressive predictive coding (NPC)~\parencite{liu_nonautoregressive_2020}, time masking is introduced through masked convolution blocks. Taking inspiration from XLNet~\parencite{yang_xlnet_2019}, it has also been suggested that the input be reconstructed from a shuffled version~\parencite{song_speechxlnet_2020} to address the discrepancy between pre"=training and fine"=tuning of masking-based approaches.

>>>>

A drawback of APC is that it encodes information only from previous timesteps
and not the entire input.
DeCoAR~\parencite{ling_deep_2020} combines the bidirectionality of the popular NLP model
ELMo~\parencite{peters_deep_2018} and the reconstruction objective of APC to alleviate
this issue and allow encoding information from the entire input. 
It uses a forward LSTM $f_1(\cdot)$ to encode $X_{[1,t]}$ and a backward LSTM
$f_2(\cdot)$ to encode $X_{[t+k,T]}$, where $k>1$: 
\begin{gather}
    H_{[1,t]} = f_1(X_{[1,t]}) \enspace , \\
    H^\prime_{[t+k,T]} = f_2(X_{[t+k,T]}) \enspace , \\
    \hat{X}_{[t+1,t+k-1]} = g(h_t, h^\prime_{t+k}) \enspace .
\end{gather}
The input feature vector used in the downstream tasks is the concatenation of
$h_{t}$ and $h^\prime_{t}$.

@@

From a high-level perspective, the training phase of models using masked
reconstruction can be formulated as
\begin{align}
    H &= f(m(X)) \enspace , \\
    \hat{x}_t &= g(h_{t}) \enspace , \\
    \mathcal{L}_t &= \lVert \hat{x}_{t} - x_{t} \rVert_1 \enspace .
\end{align}
\edit{The exact masking policy defined by $m(\cdot)$ differs from model to model and will be discussed further below.}
The function $f(\cdot)$ is typically a Transformer encoder~\parencite{liu_mockingjay_2020,jiang_improving_2019,liu_masked_2020}, but recurrent neural networks have also been used~\parencite{wang_unsupervised_2020}. \edit{In general, the Transformer encoder architecture has been adopted widely by self"=supervised models for speech within all three surveyed categories.} \edit{The function $g(\cdot)$ is usually a linear projection or a multilayer perceptron (MLP)}. Finally, the loss $\mathcal{L}_t$ is commonly computed only for masked timesteps in order to discourage the model from learning an identity mapping.

The masking policies used in NLP can be adapted to speech by considering a speech \edit{segment} equivalent to a token in a sentence; indeed, the masking strategy of BERT has also been used for speech pre"=training~\parencite{liu_mockingjay_2020}.
In the standard BERT masking policy, each token is masked independently at random. However, for speech, masking a single \edit{sample or spectrogram frame results in a largely} trivial reconstruction task \edit{since, as discussed in %\cref{par:apc}
the paragraph on autoregressive prediction, the smoothness of audio signals may encourage the model to learn to simply interpolate neighboring frames.} Therefore, it is common to mask chunks of consecutive frames~\parencite{liu_mockingjay_2020,jiang_further_2021}.

@@

Some studies explore alternatives to masking the input directly. In non"=autoregressive predictive coding (NPC)~\parencite{liu_nonautoregressive_2020}, time masking is introduced through masked convolution blocks. Taking inspiration from XLNet~\parencite{yang_xlnet_2019}, it has also been suggested that the input be reconstructed from a shuffled version~\parencite{song_speechxlnet_2020} to address the discrepancy between pre"=training and fine"=tuning of masking"=based approaches.
